MIP-GNN: A data-driven tool for guiding combinatorial solvers

### 2020-08-06 paper/main.tex
Rest of experiments.

		\State Call oracle: $\vec{x} \leftarrow \cO(\vec{p}\trans \vec{A} \vec{x} \geq \vec{p}\trans \vec{b})$, \textbf{if} $
		\vec{x} = \emptyset$ \Return  \texttt{non-feasible}
		\State Compute error signal $\vec{e}$, where
		\begin{equation*}
		\vec{e}_j \leftarrow \nicefrac{1}{\rho}\,(\vec{A}_j\trans \vec{x}(t) - \vec{b}_j)   
		\end{equation*}
		\State Perform gradient descent by $\vec{w}_i \leftarrow (1 - \eta \vec{e}_i) \vec{w}_i$ 
		\State Normalize weights $\vec{p}_j \leftarrow \nicefrac{\vec{w}_j}{\boldsymbol{\Gamma}(t)} $  for $i$ in $[m]$, where $\boldsymbol{\Gamma}(t) = \sum_{i \in [m]} \vec{w}_i$
		\State Update solution $\vec{\bar{x}} \leftarrow \vec{\bar{x}} + \vec{x}$
		\EndFor
		\State \Return Average over solution $ \nicefrac{\vec{\bar{x}}}{T} $
	\end{algorithmic}
	\caption{MWU for the LP feasibility problem.}
	\label{alg:as}
\end{algorithm}
Same algorithm as above interpreted as a message passing algorithm:
\begin{algorithm}[H]\mbox{\hfill}
	\\\textbf{Input:} Biparite constraint graph $B(I)$, $\varepsilon > 0$,  stepsize $\eta > 0$, scaling constant $\rho$. \\
	\textbf{Output:} $\vec{\bar{x}}$ satisfying~\cref{epsfeas} or \texttt{non-feasible}.
	\begin{algorithmic}[1]
		\State Initialize weights $\vec{w}_j \leftarrow 1$ for each constraint node
		\State Initialize probabilities $\vec{p}_j \leftarrow \nicefrac{1}{m}$ for each constraint node
		\State Set $T$ to according~\cref{mwubound}
		\For{$t \text{ in } [T]$}
		\State For each constraint node $\vec{c}_j$ send $\vec{p}_j$ to adjacent node variable \Comment{Constraint to variable pass}
		\Statex
		\State Update each variable node $\vec{v}_i$ based on output $\vec{x}_i$ of oracle using $\vec{p}$
		\State Send $\vec{v}_i$ to each adjacent constraint, compute error signal $\vec{e}_i$ for each constraint $\vec{c}_j$\Comment{Variable to constraint pass}
		\begin{equation*}
		\vec{e}_j \leftarrow \nicefrac{1}{\rho}\,\Big(\sum_{i \in N(j)} \label{key}\vec{A}_{ji}  \vec{v}_i \Big) - \vec{b}_j   
		\end{equation*}
		\State Perform gradient descent by $\vec{w}_i \leftarrow (1 - \eta \vec{e}_i) \vec{w}_i$ 
		\State Normalize weights $\vec{p}_j \leftarrow \nicefrac{\vec{w}_j}{\boldsymbol{\Gamma}(t)} $  for $i$ in $[m]$, where $\boldsymbol{\Gamma}(t) = \sum_{i \in [m]} \vec{w}_i$
		\State Update solution $\vec{\bar{x}} \leftarrow \vec{\bar{x}} + \vec{x}$
		\EndFor
		\State \Return Average over solution $ \nicefrac{\vec{\bar{x}}}{T}$
	\end{algorithmic}
	\caption{MWU (Message passing version) for the LP feasibility problem.}
	\label{alg:as}
\end{algorithm}

@@

\begin{algorithm}[H]\mbox{\hfill}
	\\\textbf{Input:}  Training set $\cS$, $\varepsilon > 0$, number of epochs $E$, number of rounds $T$, stepsize $\eta > 0$, scaling constant $\rho$.  \\
	\textbf{Output:} A trained model $f_{\boldsymbol{\theta}} \colon \cI \to [0,1]^n$.
	\begin{algorithmic}[1]
		\State Initialize $\vec{v}_i^{(0)}$, $\vec{c}_i^{(0)}$
		\State Initialize parameters $\boldsymbol{\theta} = (\boldsymbol{\theta}_{\text{V}}$, $\boldsymbol{\theta}_{\text{C}}$, $\boldsymbol{\theta}_{\text{X}})$
		\State Set weights $\vec{w}_j^{(0)} \leftarrow 1$, $\vec{p}_j^{(0)} \leftarrow \nicefrac{1}{m}$ for $j$ in $[m]$
		\For{$e \text{ in } [E]$}
		\State Sample $I = (\vec{c}, \vec{A}, \vec{b})$ with variable bias $\vec{\bar{b}}$ uniformly and at random from $\cS$, inducing the bipartite graph $B(I)$
		\For{$t \text{ in } [T]$}
		\State $\vec{v}_i^{(t)} \leftarrow {f}^{(t)}_{\text{V}} \hspace{-1pt} \big( \big\{ \hspace{-4.4pt} \big\{ \big( \vec{v}^{(t-1)}_i, \vec{c}^{(t-1)}_j, \vec{p}^{(t-1)}_j, \vec{A}_{ji} \big)\hspace{-1pt} \colon c_j \in N(v_i) \big\} \hspace{-4.4pt} \big\} \big)$ for all $i$ in $[n]$ 		
		\Comment{Constraint to variable pass}
		\State $\vec{x}_i^{(t)} \leftarrow {f}^{(t)}_{\text{X}} \hspace{-2pt} \left(\vec{v}_i^{(t-1)} \right)$ for all $i$ in $[n]$ \Comment{Generate variable assigment}
		\Statex
		\Statex
		\State $\vec{c}_j^{\hspace{1pt}(t)} \leftarrow {f}^{(t)}_{\text{C}} \hspace{-2pt} \left( \left\{ \hspace{-4.4pt} \left\{ \left( \vec{c}^{(t-1)}_j, \vec{v}^{(t)}_i, \vec{x}^{(t)}_i, \vec{A}_{ji}, \vec{b}_j \right)\hspace{-2pt} \colon i \in N(c_j) \right\} \hspace{-4.4pt} \right\} \right)$ for all $j$ in $[m]$ 		\Comment{Variable to constraint pass}
		\State $\vec{e}_j^{(t)} \, \leftarrow \nicefrac{1}{\rho}\,\Big(\sum_{i \in N(j)} \label{key}\vec{A}_{ji}  \vec{v}_i \Big) - \vec{b}_j$
		%\Statex
		\State $\vec{w}_j^{(t)} \leftarrow ( 1 -  \eta \vec{e}^{(t)}_j) \vec{w}_j^{(t-1)} $ 
		\State $\vec{p}_j \leftarrow \nicefrac{w_j^{(t)}}{\boldsymbol{\Gamma}(t)} $, where $\boldsymbol{\Gamma}(t) = \sum_{j \in [m]} \vec{w}^{(t)}_j$
		\State Update solution $\vec{\bar{x}} \leftarrow \vec{\bar{x}} + \vec{x}$
		\EndFor
		\State $\vec{\bar{x}} \leftarrow \nicefrac{1}{T} \sum_{t \in [T]} \vec{x}(t) $
		\State $L \leftarrow L + \ell(\vec{\bar{x}}, \vec{\bar b})$ 
		\State Gradient descent on $\nicefrac{1}{T} L$ with regard to $\boldsymbol{\theta}$
		\EndFor
		\State \Return $\boldsymbol{\theta}$

>>>>

		\State Call oracle: $\vec{x} \leftarrow \cO(\vec{p}\trans \vec{A} \vec{x} \geq \vec{p}\trans \vec{b})$, \textbf{if} $
		\vec{x} = \emptyset$ \Return  \texttt{non-feasible}
		\State Compute error signal $\vec{e}$, where
		\begin{equation*}
		\vec{e}_j \leftarrow \nicefrac{1}{\rho}\,(\vec{A}_j\trans \vec{x}(t) - \vec{b}_j)   
		\end{equation*}
		\State Perform gradient descent by $\vec{w}_i \leftarrow (1 - \eta \vec{e}_i) \vec{w}_i$ 
		\State Normalize weights $\vec{p}_j \leftarrow \nicefrac{\vec{w}_j}{\boldsymbol{\Gamma}(t)} $  for $i$ in $[m]$, where $\boldsymbol{\Gamma}(t) = \sum_{i \in [m]} \vec{w}_i$
		\State Update solution $\vec{\bar{x}} \leftarrow \vec{\bar{x}} + \vec{x}$
		\EndFor
		\State \Return Average over solution $ \nicefrac{\vec{\bar{x}}}{T} $
	\end{algorithmic}
	\caption{MWU for the LP feasibility problem.}
	\label{alg:as}
\end{algorithm}
Same algorithm as above interpreted as a message passing algorithm:
\begin{algorithm}[H]\mbox{\hfill}
	\\\textbf{Input:} Biparite constraint graph $B(I)$, $\varepsilon > 0$,  stepsize $\eta > 0$, scaling constant $\rho$. \\
	\textbf{Output:} $\vec{\bar{x}}$ satisfying~\cref{epsfeas} or \texttt{non-feasible}.
	\begin{algorithmic}[1]
		\State Initialize weights $\vec{w}_j \leftarrow 1$ for each constraint node
		\State Initialize probabilities $\vec{p}_j \leftarrow \nicefrac{1}{m}$ for each constraint node
		\State Set $T$ to according~\cref{mwubound}
		\For{$t \text{ in } [T]$}
		\State For each constraint node $\vec{c}_j$ send $\vec{p}_j$ to adjacent node variable
		\Statex
		\State Update each variable node $\vec{v}_i$ based on output $\vec{x}_i$ of oracle using $\vec{p}$
		\State Send $\vec{v}_i$ to each adjacent constraint, compute error signal $\vec{e}_i$ for each constraint $\vec{c}_j$
		\begin{equation*}
		\vec{e}_j \leftarrow \nicefrac{1}{\rho}\,\Big(\sum_{i \in N(j)} \label{key}\vec{A}_{ji}  \vec{v}_i \Big) - \vec{b}_j   
		\end{equation*}
		\State Perform gradient descent by $\vec{w}_i \leftarrow (1 - \eta \vec{e}_i) \vec{w}_i$ 
		\State Normalize weights $\vec{p}_j \leftarrow \nicefrac{\vec{w}_j}{\boldsymbol{\Gamma}(t)} $  for $i$ in $[m]$, where $\boldsymbol{\Gamma}(t) = \sum_{i \in [m]} \vec{w}_i$
		\State Update solution $\vec{\bar{x}} \leftarrow \vec{\bar{x}} + \vec{x}$
		\EndFor
		\State \Return Average over solution $ \nicefrac{\vec{\bar{x}}}{T}$
	\end{algorithmic}
	\caption{MWU (Message passing version) for the LP feasibility problem.}
	\label{alg:as}
\end{algorithm}

@@

\begin{algorithm}[H]\mbox{\hfill}
	\\\textbf{Input:}  Training set $\cS$, $\varepsilon > 0$, number of epochs $E$, number of rounds $T$, stepsize $\eta > 0$, scaling constant $\rho$.  \\
	\textbf{Output:} A trained model $f_{\boldsymbol{\theta}} \colon \cI \to [0,1]^n$.
	\begin{algorithmic}[1]
		\State Initialize $\vec{v}_i^{(0)}$, $\vec{c}_i^{(0)}$
		\State Initialize parameters $\boldsymbol{\theta} = (\boldsymbol{\theta}_{\text{V}}$, $\boldsymbol{\theta}_{\text{C}}$, $\boldsymbol{\theta}_{\text{X}})$
		\State Set weights $\vec{w}_j^{(0)} \leftarrow 1$, $\vec{p}_j^{(0)} \leftarrow \nicefrac{1}{m}$ for $j$ in $[m]$
		\For{$e \text{ in } [E]$}
		\State Sample $I = (\vec{c}, \vec{A}, \vec{b})$ with variable bias $\vec{\bar{b}}$ uniformly and at random from $\cS$, inducing the bipartite graph $B(I)$
		\For{$t \text{ in } [T]$}
		\State $\vec{v}_i^{(t)} \leftarrow {f}^{(t)}_{\text{V}} \hspace{-1pt} \big( \big\{ \hspace{-4.4pt} \big\{ \big( \vec{v}^{(t-1)}_i, \vec{c}^{(t-1)}_j, \vec{p}^{(t-1)}_j, \vec{A}_{ji} \big)\hspace{-1pt} \colon c_j \in N(v_i) \big\} \hspace{-4.4pt} \big\} \big)$ for all $i$ in $[n]$

		\State $\vec{x}_i^{(t)} \leftarrow {f}^{(t)}_{\text{X}} \hspace{-2pt} \left(\vec{v}_i^{(t-1)} \right)$ for all $i$ in $[n]$ 
		\Statex
		\Statex
		\State $\vec{c}_j^{\hspace{1pt}(t)} \leftarrow {f}^{(t)}_{\text{C}} \hspace{-2pt} \left( \left\{ \hspace{-4.4pt} \left\{ \left( \vec{c}^{(t-1)}_j, \vec{v}^{(t)}_i, \vec{x}^{(t)}_i, \vec{A}_{ji}, \vec{b}_j \right)\hspace{-2pt} \colon i \in N(c_j) \right\} \hspace{-4.4pt} \right\} \right)$ for all $j$ in $[m]$ 	
		\State $\vec{e}_j^{(t)} \, \leftarrow \nicefrac{1}{\rho}\,\Big(\sum_{i \in N(j)} \label{key}\vec{A}_{ji}  \vec{v}_i \Big) - \vec{b}_j$
		%\Statex
		\State $\vec{w}_j^{(t)} \leftarrow ( 1 -  \eta \vec{e}^{(t)}_j) \vec{w}_j^{(t-1)} $ 
		\State $\vec{p}_j \leftarrow \nicefrac{w_j^{(t)}}{\boldsymbol{\Gamma}(t)} $, where $\boldsymbol{\Gamma}(t) = \sum_{j \in [m]} \vec{w}^{(t)}_j$
		\State Update solution $\vec{\bar{x}} \leftarrow \vec{\bar{x}} + \vec{x}$
		\EndFor
		\State $\vec{\bar{x}} \leftarrow \nicefrac{1}{T} \sum_{t \in [T]} \vec{x}(t) $
		\State $L \leftarrow L + \ell(\vec{\bar{x}}, \vec{\bar b})$ 
		\State Gradient descent on $\nicefrac{1}{T} L$ with regard to $\boldsymbol{\theta}$
		\EndFor
		\State \Return $\boldsymbol{\theta}$
